Verifying Demonstrations

### 2020-07-03 paper/conclusions.tex
Edits conclusions

In this paper, we have adapted the Schnorr protocol as a
distance-bounding protocol.  It allows to construct distance-bounding
general attribute-based authentication, more general attributes than
provided by previous \ac{DB} ones.  With our contribution, Alice can
now prove more complex statements to Bob; \eg that she is older than 18 
(without revealing her actual age), has a cinema subscription which is not 
\enquote{double spent} by someone else at the same time and, at the same time, 
Bob can be sure that Alice is not just relaying messages from her older sister 
Carol or \ac{DBMF} relaying the subscription from some unsuspecting stranger.

>>>>

In this paper, we have adapted the Schnorr protocol as \iac{DB} protocol.
It allows us to construct \ac{DB}, general attribute-based authentication; more 
general attributes than provided by previous \ac{DB} ones.
With our contribution, Alice can now prove more complex statements to Bob; \eg 
that she is older than 18 (without revealing her actual age), has a cinema 
subscription which is not \enquote{double spent} by someone else at the same 
time~\cite[\eg][]{AnonPass} and, at the same time, Bob can be sure that Alice 
is not just relaying messages from her older sister Carol or \ac{DBMF} relaying 
the subscription from some unsuspecting stranger also waiting in the queue to 
enter.
